Tensor anisotropy as a tracer of cosmic voids

### 2015-05-05 RefereeResponse.md

Conceptual:
==

1. **It seems that part of the motivation for using FA is that it is very well correlated with lambda_1, at low lambda_1. FA is a rather interesting quantity in itself, differentiating haloes and voids from filaments and walls, but it is not clear why it should be superior to lambda_1 for void finding. The authors should more clearly articulate why this might be, if there is a reason. The FA being "conceived to quantify the anisotropy of the diffusivity of water molecules through cerebral tissue in nuclear magnetic resonance imaging" should be elaborated on; this does not clarify the usefulness of the FA for cosmologists. Conceptually, I also wonder: do filaments and walls behave differently from each other in FA, or do they both have FA ~ 1?**

2. **I did not understand the sentence at the end of Sect 2, "In this work we propose an optimal value of the threshold based on the maximization of the fractional anisotropy field in the locations label[ed] as filaments and walls," and this seems to be an important point. Is the threshold mentioned in this sentence a threshold in lambda_1, or FA? Is this the 0.95 threshold in FA? It seems to be a reasonable choice, but I do not see a sense in which it is "optimal," except that it seems to be the boundary between the FA being well-correlated with lambda_1 and not-so-well. Also, if this sentence is about the 0.95 threshold, I do not see why it "does not enter into our computations," since the boundary of many voids will depend on this threshold. It would be useful to know for what fraction of voids the limit FA = 0.95 actually affects the boundary (in the case of the largest voids, I suppose).**

3. **I do not see how the value of FA=0.65 (corresponding to lambda_1 = 0) is used "to remove ridges."**

4. **In Fig. 6, I only see a clear ridge in FA at r~r_eff in a few cases. the sentence in Sect. 5.5 "The difference between the radius where the density ridge is reached ([r/]reff = 3) and the radius of the FA ridge ([r/]reff = 1 ) ..." implies that I should see a ridge in FA at r~r_eff. Is this because the ridge is actually a 2D surface that is spherically averaged? It would be helpful to point this (or any other reasons) out. Also, the statement "This makes the FA ridge a reasonable boundary for voids compared to the traditional definition that puts the boundary at the density ridge" implies (perhaps unintentionally) that the FA ridge is a superior marker of the edge of a void than a density ridge. It is a physically different sort of ridge, and I agree that it is reasonable, but I do not see why it should be superior.**

5. **I am not convinced that the "tiny white bubbles located inside sheets" are embedded in overdense regions. Based just on Fig. 1, they could be physical, but small, voids. We also no nothing of their extent perpendicular to the plane of Fig. 1; we could just be looking of corners of much larger objects.**

6. **2D histograms of (lambda_1, delta) and (lambda_1, FA) are shown in Fig. 2, and I would appreciate also seeing a (FA, delta) 2D histogram, maybe with 1+delta on a log scale, which would help to clarify the physical meaning of FA.**

More minor things:
==

7. **I'm confused a bit about the middle panels of Fig. 1. The title, "Visual impresion for lambda_th=..." is strange. Aren't there several thresholds here? Also, what are the blue dots? Also "impresion" is misspelled.**

8. **Sect 3.3, 2nd paragraph: I do not see why "the analysis of [y]our results" shows that a fixed Cartesian mesh does not induce spurious results". It's true, that the results look reasonable, but I think it would be better to state something about the level of discreteness noise, e.g. the number of zero-density cells, or the minimum if there are none.**

9. **Sect. 5.4: The sentence "subcompensated voids have outflowing ve- locity profiles all the way up to the effective radius where the average radial density reaches the average value" is a bit confusing; this is not r_eff, right? If so, this statement seems to be an understatement (v_r >0 out to several r_eff, typically). If not, "effective" should be removed for clarity.**

10. **In Sect. 5.5, there are a few instances where I think you meant "r/r_eff =" instead of "r_eff =".**

11. **All quantities are computed at the pixel scale, ~1 Mpc/h, correct? If the authors have any insights about how the results would change if this scale were changed, it would be helpful to state them. A quantitative discussion of how some results would change with a different scale would be great, but not necessary.**

12. **Finally, about the necessity of color: Figs 4-6, as they currently are, require color, but it would be easy for the authors to use different linestyles, as well, to make color unnecessary.**

### 2015-05-13 cosmic_voids.tex
Slide of voids colored according to their effective radius instead of a random color. Little typo.

\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
%\documentclass{latex/emulateapj} 
%External Packages and personalized macros
%=========================================================================
%		EXTERNAL PACKAGES
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
%\usepackage[section]{placeins}
\usepackage {graphicx}
%\usepackage{graphics}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{caption}
%Non reposionated tables
\usepackage{float}
\restylefloat{table}
%Multiple columns support for tables
\usepackage{array}
\usepackage{booktabs}
\setlength{\heavyrulewidth}{1.5pt}
\setlength{\abovetopsep}{4pt}

@@

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}

@@

The tracer that we use to define the voids is the fractional
anisotropy (FA) computed from the set of eigenvalues of the tensor
under consideration. 
The FA was initially introduced by \citet{Basser95} to quantify the
anisotropy degree of the diffusivity of water molecules through
cerebral tissue in nuclear magnetic resonance
imaging and \citet{Libeskind13} introduced this concept in the context
of Cosmic Web classification schemes.

@@

  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{delta_L1.pdf}  
  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{FA_L1.pdf}

  \captionof{figure}{\small Overdensity (left) and Fractional
    Anisotropy (right) with respect to the eigenvalue $\lambda_1$ 
    for each web scheme (T-Web, continous lines. V-Web, dashed lines) calculated 
    over all grid cells in the Bolshoi simulation. 
    Thick central lines are the median and filled regions include
    $50\%$ of the cells in each bin.
    This information is necesary to define void boundaries in
    the watershed algorithm. 
    The vertical lines show the equivalent threshold values for the
    T-Web and V-web in order to have voids composed by cells with
    Fractional Anisotrop equal or less than $0.95$. 
   This threshold on the eigenvalues does not influence our
   computations. 
   We show it as a guide to readers familiar with the
   order of magnitude expectation for this threshold.}
  \label{fig:L1_correlations}

@@

The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
conceived to quantify the anisotropy of the diffusivity of water
molecules through cerebral tissue in nuclear magnetic resonance imaging. 
Here we present the FA, much in the same way as \citet{Libeskind13},
to use it as a tracer of cosmic voids.

@@

@@

The difference between the radius where the density ridge is reached 
($r_{\rm eff}=3$) and the radius of the FA  ridge ($r_{\rm eff}=1$ )
justifies in a more quantiative way the qualitative argument
we present in sub-section \ref{subsec:watershed} to define void boundaries in
our method.  
Namely that as we increase the void boundary, we reach
first middle density walls, before reashing high density structures
associated with high anisotropy. 
This makes the FA ridge a reasonable
boundary for voids compared to the traditional definition that puts
the boundary at the density ridge.

>>>>

\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
%\documentclass{latex/emulateapj} 
%External Packages and personalized macros
%=========================================================================
%		EXTERNAL PACKAGES
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
%\usepackage[section]{placeins}
\usepackage {graphicx}
%\usepackage{graphics}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{caption}
%Non reposionated tables
\usepackage{float}
\restylefloat{table}
%Multiple columns support for tables
\usepackage{array}
\usepackage{booktabs}
\setlength{\heavyrulewidth}{1.5pt}
\setlength{\abovetopsep}{4pt}
\pdfminorversion=5

@@

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
\newcommand{\before}[1]{\textcolor{red}{ #1}}
\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}

@@

% CORRECTION: ISSUE 1 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

\before{ The tracer that we use to define the 
voids is the fractional anisotropy (FA) computed from the set of 
eigenvalues of the tensor under consideration. 
The FA was initially introduced by \citet{Basser95} to quantify the
anisotropy degree of the diffusivity of water molecules through
cerebral tissue in nuclear magnetic resonance
imaging and \citet{Libeskind13} introduced this concept in the context
of Cosmic Web classification schemes.}

\after{The tracer that we use to define the voids is the fractional
anisotropy (FA) computed from the set of eigenvalues of the tensor
under consideration. 
The FA was initially introduced by \citet{Basser95} to quantify the
anisotropy degree of the diffusivity of water molecules through
cerebral tissue in nuclear magnetic resonance imaging, thereby allowing to 
detect structures that restrict the otherwise isotropic Brownian movement 
of water molecules. Taking into account that this process is identical to 
the velocity shear in the large-scale matter distribution, 
\citet{Libeskind13} introduced the concept of the FA in the context of 
Cosmic Web classification schemes.}

%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{delta_L1.pdf}  
  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{FA_L1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{FA_delta.pdf}

  \captionof{figure}{\small Overdensity (upper left) and Fractional
    Anisotropy (upper right) with respect to the eigenvalue $\lambda_1$ 
    for each web scheme (T-Web, continous lines. V-Web, dashed lines) 
    calculated over all grid cells in the Bolshoi simulation. 
    Thick central lines are the median and filled regions include
    $50\%$ of the cells in each bin. This information is necessary to 
    define void boundaries in the watershed algorithm. The vertical lines 
    show the equivalent threshold values for the T-Web and V-web in order 
    to have voids composed by cells with Fractional Anisotrop equal or 
    less than $0.95$. This threshold on the eigenvalues does not influence 
    our computations. We show it as a guide to readers familiar with the
    order of magnitude expectation for this threshold.}
  \label{fig:L1_correlations}

@@

% CORRECTION: ISSUE 1 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

\before{The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
conceived to quantify the anisotropy of the diffusivity of water
molecules through cerebral tissue in nuclear magnetic resonance imaging. 
Here we present the FA, much in the same way as \citet{Libeskind13},
to use it as a tracer of cosmic voids.}

\after{The fractional anisotropy (FA), as developed by \citet{Basser95}, 
was conceived to quantify the anisotropy of the diffusivity of water
molecules through cerebral tissue in nuclear magnetic resonance imaging. 
In this manner, barriers such as microtubules and cell membranes, that 
restrict the otherwise isotropic Brownian motion of water molecules, can 
be detected. In a cosmological context, the problem of finding structures 
is very similar, where filaments and sheets restrict the otherwise 
isotropic collapsing/expanding dynamics of the matter. Taking this into 
account, we present here the FA, much in the same way as \citet{Libeskind13}, 
to use it as a tracer of cosmic voids.}

%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

% CORRECTION: ISSUE 1 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\after{At this point, the eigenvalue $\lambda_1$ and the FA appear to be
equally potential candidates for tracing cosmic voids, however, }
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

The difference between the radius where the density ridge is reached 
($r_{\rm eff}=3$) and the radius of the FA  ridge ($r_{\rm eff}=1$ )
justifies in a more quantiative way the qualitative argument
we present in sub-section \ref{subsec:watershed} to define void boundaries in
our method.  
Namely that as we increase the void boundary, we reach
first middle density walls, before reaching high density structures
associated with high anisotropy. 
This makes the FA ridge a reasonable
boundary for voids compared to the traditional definition that puts
the boundary at the density ridge.
